\documentclass[12pt,a4paper,sans]{moderncv}

\moderncvstyle{classic} % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{purple}    % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'

\usepackage[scale=0.85]{geometry}
\usepackage{xpatch}

\name{Gabriele}{da Soler Vieira}
\title{Software Developer}
\address{Cocal do Sul -- SC, Brazil}
\phone[mobile]{+55 (48) 99670-1019}
\email{gabriele.dasolervieira@gmail.com}
\social[linkedin]{gabrieledasoler}
\social[github]{gabrielesoler}

\makeatletter
\xpatchcmd{\makehead}{\titlestyle{~|~\@title}}{\par\vskip2ex\titlestyle{\huge \@title}}{}{}
\makeatother

\begin{document}

\makecvtitle

\section{Skills}

\begin{tabular*}{\textwidth}{@{\extracolsep{2mm}} r l}
	\textbf{Languagues} & Typescript, Javascript, C\#, SQL. \\
	\textbf{Technologies} & React Native, ReactJS, Ext.Js, VueJS. \\
\end{tabular*}

\section{Summary}
{I am a frontend developer with 2+ years of professional experience.
\\
Graduated in Technology in Systems Analysis and Development, I began my professional journey in 2021 through an internship, where I worked with Typescript and Vue.js. In 2022, I took a significant step in my career by assuming the role of Junior Front-End Developer, expanding my scope to include Back-End activities.
\\
I have experience and proficiency in React JS, Ext.js, Typescript, Javascript, Vue.js, and C\#, as well as proficiency in English. I am passionate about technology and am always seeking to improve my skills.}

\section{Experience}
\cventry{April/2022 -- Presente}{Fullstack Developer}{Useall Software}{Criciúma-SC (Remote)}{}{
  At Useall, I work on the frontend development of software aimed at managing electricity distributors, specifically the financial part of the system, I'm currently also responsible for backend activities. My responsibilities include:
  \begin{itemize}
    \item Frontend and backend development, creating new features and providing maintenance.
    \item Participating in the vertical's sprint planning meetings.
  \end{itemize}
  \bigskip
  Skills: Front-End Development · C\#  · ExtJs · Oracle Database · JavaScript
}

\cventry{Mar/2021 -- Oct/2021}{Intern}{News Soft House}{Tubarão-SC}{}{
  At News Soft, I worked as an intern, developing some simple tasks on the frontend development.
  \bigskip
  Skills: VueJS · Typescript 
}

\section{Education}
\cventry{2019 -- 2023}{Systems Analysis and Development Technology}{SENAC}{Criciúma -- SC}{}{}

\section{Languages}
\cvitemwithcomment{English}{Advanced}{Can understand and talk about complex subjects.}
\cvitemwithcomment{Portuguese}{Native}{}

\end{document}
